### 2021-05-31 thesis/tex/sterileTheory.tex
update

% \documentclass{thesis}
% \usepackage[margin=0.5in]{geometry}
% \usepackage{subcaption}
% \input{commands}

% \begin{document}
\section{The Sterile State}\label{sec:anomalies}
In 1996, the LSND experiment reported an excess of $\ane$ events from an $\anm$ beam~\cite{lsnd}. The anomaly was consistent with a fourth
neutrino state with $\dm[41] > \SI{0.03}{\eV \squared}$. Nine years later, MiniBooNE not only reproduced the $\ane$ anomaly, but saw the excess in The
$\ne$ events too. Together with the so-called reactor and gallium analomalies, there were indications that both appearance and disappearance
anomalies might be remedied by a fourth mass state.

@@

\subsection{Sterile Signals}
Since the new neutrino does not interact weakly, how do we then detect its signal? If the sterile mixing angle $\theta_{i4}$ is non-zero, 
we allow the sterile mass state to mix with the active state $i$. The most interesting case is when $\theta_{24} \neq 0$, 
which for $\dm[41] \sim \si{\eV \squared}$ gives rise to a resonant disappeareance in the $\bar\mu \bar\mu$ sector, shown in Fig.~\ref{fig:sterile_resonance}.

@@

So for a \si{\eV}-scale sterile neutrino and a non-zero $\theta_{24}$, we expect a \si{\TeV} $\anm$ disappearance.
The resonance dip is affected by the value of $\dm[41]$ and $\theta_{24}$ as shown in Fig.~\ref{fig:resonance_shift}.
We see how the value of $\dm[41]$ shifts the peak, while the mixing angle adjusts its strength. 
%TODO: more? mention that Pmm=1 at TeV for 3+0

% \newpage
% \bibliographystyle{elsarticle-num}
% \bibliography{ref}
% \end{document}

>>>>

% \input{commands}\begin{document}
\section{The Sterile State}\label{sec:anomalies}
In 1996, the LSND experiment reported an excess of $\ane$ events from an $\anm$ beam~\cite{lsnd}. The anomaly was consistent with a fourth
neutrino state with $\dm[41] > \SI{0.03}{\eV \squared}$. Nine years later, MiniBooNE not only reproduced the $\ane$ anomaly, but saw the excess in The
$\ne$ events too. Together with the so-called reactor and gallium analomalies, there were indications that both appearance and disappearance
anomalies might be remedied by a fourth mass state.

@@

\subsection{Sterile Signals}
Since the new neutrino does not interact weakly, how do we then detect its signal? If the sterile mixing angle $\theta_{i4}$ is non-zero, 
we allow the sterile mass state to mix with the active state $i$. The most interesting case is when $\theta_{24} \neq 0$, 
which for $\dm[41] \sim \si{\eV \squared}$ gives rise to a resonant disappeareance in the for $P_{\anm\anm}$, shown in Fig.~\ref{fig:sterile_resonance}.

@@

So for a \si{\eV}-scale sterile neutrino and a non-zero $\theta_{24}$, we expect a \si{\TeV} $\anm$ disappearance.
The resonance dip is affected by the value of $\dm[41]$ and $\theta_{24}$ as shown in Fig.~\ref{fig:resonance_shift}.
We see how the value of $\dm[41]$ shifts the peak, while the mixing angle adjusts its strength. 
TODO: more? mention that Pmm=1 at TeV for 3+0

% \newpage\bibliographystyle{elsarticle-num}\bibliography{ref}\end{document}
